---
title: "R S3/S4 class/object"
author: Weiyang Tao (weiyangtao1513@gmail.com)
output:
  html_document:
    df_print: paged
---
# Object
Everything in R is an object.

```{r}
a = 1
b = "character"
c = function(x) x
d = NULL
e = TRUE

```


# Class

```{r}
a = 1:10
str(a)
class(a) = "classA"
str(a)
```


# S3 class/object

```{r}
rm(list = ls( all.names = TRUE))
b0 = c("a", "b", "c")
str(b0)

objectB = structure(c("a", "b", "c"), class = "classB")
str(objectB)
```
Let's print objectB using "print" function.
```{r}
print(objectB)
```


# S3 function/method
```{r}
print.classB = function(x){
  cat("This is a classB object\n")
  print.default(x)
}
print.classB(objectB)
```


Let's print objectB using "print" function again.
```{r}
print(objectB) # the same as print.classB
```



# S4 class

```{r}
ls(all.names = T)
rm(list = ls( all.names = TRUE))
setClass(Class = "Class4", 
         representation = representation(first = "numeric",
                                         second = "character"))
ls(all.names = T)
.__C__Class4
str(.__C__Class4)
```


# S4 object
Create an S4 object using the default values
```{r}
# Using the default values
new("Class4")
```


Create an S4 object using the default values
```{r}
# Using the default values
object4 = new("Class4", first = 1:5, second = letters)
object4
```


Set Generic
```{r}
setGeneric(name = "fun", def = function(object, ...) standardGeneric("fun"))
```


What code is in function "fun"?
```{r}
fun
```


Can we apply function "fun" on "object4"?
```{r, eval=FALSE}
fun(object4)
```

# Define a method for object4
```{r}
# "object" argument in the function must be the same as in the generic
setMethod(f = "fun", signature = signature("Class4"), 
          definition = function(object){
            cat("first:\n")
            cat(object@first, "\n\n")
            cat("second:\n")
            cat(object@second, "\n")
          })
```


Can we use "fun" on "object4" now?
```{r}
fun(object4)
```


What code is in function "fun" now?
```{r}
fun
```
*The same code!! *
- - - - - 

# Can we get the code of a method?

```{r}
# devtools::install_github("paodan/funcTools")
library(funcTools)
tmp = funCode(fun)
tmp@fS4@fcn$Class4
```


Let's see if it is the same output as function "fun" itself.
```{r}
print(tmp@fS4@fcn$Class4)
tmp@fS4@fcn$Class4(object4)
```

```{r}
fun(object4)
```

# Where is the S3 method actually stored?
To understand where S4 methods are stored, let's start by an S3 method.
```{r}
print.classB = function(x){
  cat("This is a classB object\n")
  print.default(x)
}
environment(print.classB)
```
The environment of print.classB is global environment.


What about an S4 function?
```{r}
env = environment(fun)
env
```
"env" is not the global environment.


But the parent environment of "env" is.
```{r}
parent.env(env)
```


The methods are stored in the '.MTable' or '.AllMTable' variable of 
the 'env' environment.
```{r}
envMTable = get(".MTable", envir = environment(fun))
envMTable
```


The "envMTable" is an environment of methods. And you can transform it to a
list of functions.

```{r}
envList = as.list(envMTable)
envList
```

