---
title: "R S3/S4 class/object"
author: Weiyang Tao (weiyangtao1513@gmail.com)
output:
  html_document:
    df_print: paged
---
# Object
Everything in R is an object.

```{r}
a = 1
b = "character"
c = function(x) x
d = NULL
e = TRUE

```

# Class

```{r}
a = 1:10
str(a)
class(a) = "classA"
str(a)
```

# S3 class/object

```{r}
rm(list = ls( all.names = TRUE))
b0 = c("a", "b", "c")
str(b0)

objectB = structure(b0, class = "classB")
str(objectB)
```
Let's print objectB using "print" function.
```{r}
print(objectB)
```


# S3 function/method
```{r}
print.classB = function(x){
  cat("This is a classB object\n")
  print.default(x)
}
print.classB(objectB)
```

Let's print objectB using "print" function again.
```{r}
print(objectB) # the same as print.classB
```



# S4 class

```{r}
ls(all.names = T)
rm(list = ls( all.names = TRUE))
setClass(Class = "Class4", 
         representation = representation(first = "numeric",
                                         second = "character"))
ls(all.names = T)
.__C__Class4
str(.__C__Class4)
```

# S4 object
Create an S4 object using the default values
```{r}
# Using the default values
new("Class4")
```
Create an S4 object using the default values
```{r}
# Using the default values
object4 = new("Class4", first = 1:5, second = letters)
object4
```

Set Generic
```{r}
setGeneric(name = "fun", function(object, ...) standardGeneric("fun"))
```
What code is in function "fun"?
```{r}
fun
```

Can we use "fun" on "object4"?
```{r}
# fun(object4)
```

# Define a method for object4
```{r}
# "object" argument in the function must be the same as in the generic
setMethod("fun", signature = signature("Class4"), 
          definition = function(object){
            cat("first:\n")
            cat(object@first, "\n\n")
            cat("second:\n")
            cat(object@second, "\n")
          })
```


Can we use "fun" on "object4" now?
```{r}
fun(object4)
```


What code is in function "fun" now?
```{r}
fun
```
*The same code!! *

# Can we get the code of a method?

```{r}
# devtools::install_github("paodan/funcTools")
library(funcTools)
tmp = funCode(fun)
tmp@fS4@fcn$Class4
```
Let's see if it is the same output as function "fun" itself.
```{r}
print(tmp@fS4@fcn$Class4)
tmp@fS4@fcn$Class4(object4)
```

